%-------------------------
% Modified CV from Jake's resume
% Starts modification at line 108
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\cvlink}[2]{\href{#1}{\underline{#2}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape JARETH JAZIEL MOO PAN} \\ \vspace{5pt}
    \small +52 999 610 6547 $|$ 
    \cvlink{mailto:jarethmoo@gmail.com}{jarethmoo@gmail.com} $|$ 
    \cvlink{https://linkedin.com/in/jareth-moo-6b8500271}{LinkedIn} $|$
    \cvlink{https://github.com/JarethJaziel}{GitHub} $|$
    \cvlink{https://jarethjaziel.github.io/Jareth.dev/}{Jareth.dev}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
Software Engineering student with experience in backend development using Java and Spring Boot, REST API design, and full-stack web application development with Angular. Experienced in cloud deployment and relational database design. Interested in backend development, software architecture, and distributed systems.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Autonomous University of Yucatan (UADY)}{Mérida, Yucatán, Mexico}
      {B.S. in Software Engineering (In progress)}{2023 -- Present}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, PHP, Python, JavaScript, SQL, HTML/CSS.}\\
     \textbf{Frameworks/Libraries}{: Spring Boot, Angular, LibGDX.}\\
     \textbf{Databases}{: PostgreSQL, MySQL.}\\
     \textbf{Tools}{: Git, GitHub, Gradle, Maven, SonarQube, RabbitMQ, phpMyAdmin.}\\
     \textbf{Concepts}{: REST APIs, Object-Oriented Programming (OOP), Client-Server Architecture, Relational Database Design, Git Version Control.}\\
     \textbf{Spoken Languages}{: Spanish (Native), English (B2).}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Relevant Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Devotional Web App} $|$ \emph{Spring Boot, Angular, Render, PostgreSQL, GitHub Pages} $|$
        \cvlink{https://jarethjaziel.github.io/Devo-app/}{Demo} $|$
        \cvlink{https://github.com/JarethJaziel/Devo-Service}{Backend} $|$
        \cvlink{https://github.com/JarethJaziel/Devo-app}{Frontend}}{2026}
          \resumeItemListStart
                \resumeItem{Designed and developed a full-stack web application for the publication and management of daily devotionals.}
                \resumeItem{Implemented a REST API with Spring Boot and a dynamic frontend interface using Angular.}
                \resumeItem{Designed the relational database schema in PostgreSQL.}
                \resumeItem{Deployed the application to the cloud using Render and GitHub Pages.}
          \resumeItemListEnd
          
    
    \resumeProjectHeading
    {\textbf{Abyss Battle (2D Game)} $|$ \emph{Java, LibGDX, Gradle, SonarQube} $|$
    \cvlink{https://github.com/JarethJaziel/Abyss_Battle_Java_Game}{Repository}}{2025}
    \resumeItemListStart
        \resumeItem{Designed and developed a 2D combat video game using the LibGDX framework in Java.}
        \resumeItem{Implemented project architecture and managed dependencies through Gradle.}
        \resumeItem{Utilized SonarQube to analyze code quality metrics and improve maintainability.}
        \resumeItem{Implemented game mechanics, entity management, and event handling within the engine using LibGDX.}
    \resumeItemListEnd
    

    \resumeSubHeadingListEnd

%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Youth Ministry Leadership} $|$ \emph{El Mesias Baptist Church}}{2020 -- Present}
    \resumeItemListStart
        \resumeItem{Collaborated in coordinating activities for teen and youth groups.}
        \resumeItem{Participated in the organization of camps and group events, supporting activities, logistics, and participant guidance.}
        \resumeItem{Developed leadership, communication, and teamwork skills.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Mathematics Tutoring}}{}
    \resumeItemListStart
        \resumeItem{Provided mathematics tutoring to middle and high school students, explaining concepts and guiding problem-solving sessions.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}